### 2014-09-15 tags/2014-pre-release/htdocs/basicuser.tex
Tag for Sept 2014 trunk
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2463 40876441-3496-0410-a613-a2fca35b2ae2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  user.tex
%
%  The 'user' section which holds an overview, and discusses
%  compilation and running.
%
%  $Id$
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2010 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

\subsection{Overview}

We aim to provide a robust and portable code, written in C, which
can be used to perform serial and scalable parallel simulations of
complex fluid systems based around hydrodynamics via the Lattice
Boltzmann method. Complex fluids are introduced via a free energy,
of which a number of different examples are available. The preferred
method of dealing with the corresponding order parameter equations
is now by using finite difference. However, for the case of a binary
fluid, the `full LB' approach, using two distributions, is retained
as an option for the time being.

\subsection{Availability}

Under the auspices of the CCPs (Collaborative Computational Projects),
and in particular CCP5, we have a CCPForge project account at

\texttt{http://ccpforge.cse.rl.ac.uk/}

This provides controlled access to known persons and uses version
control via SVN, and includes bug
tracking, and so on. The CCPForge SVN is not available to the public
at the present time. You need to create an account at CCPForge, and
let me or Juho know the username so you can be added to the access list.

To download the entire code, you need
\begin{verbatim}
svn checkout --username <user> http://ccpforge.cse.rl.ac.uk/svn/ludwig
\end{verbatim}
where \texttt{<user>} is replaced by your CCPForge user name.
Note that this will download all the existing tags and branches
into a new directory named \texttt{ludwig}, as well as the main code!
On success, you should see three directories
\begin{verbatim}
$ ls ludwig
branches  tags      trunk
\end{verbatim}
The main code is in the \texttt{trunk} subdirectory. This documentation is
found in the file \texttt{trunk/htdocs/ludwig.tex}, unit tests are in
the directory \texttt{trunk/tests}, and the utilities are in
\texttt{trunk/util}, and so on.

If you do not want all the tags and branches (which take up a certain amount
of space), you can specify that you
want only the trunk, e.g.,
\begin{verbatim}
svn co --username <user> http://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk
\end{verbatim}
in which case you will get a new directory called \texttt{trunk} containing
the source files. All the instructions below refer to paths relative to
this trunk directory.

If you have problems, it may be worth while looking at the issue
tracker on the project web page. It would be useful if all issues
could be reported via this mechanism. If you e-mail me, I will just
insert your e-mail into the issue tracker!

\subsection{Compilation}

Locate your local C compiler. The following example uses \texttt{gcc}
in serial, and \texttt{mpicc} in parallel. For MPI in particular,
local details may vary.

The other thing required by the Makefile is the utility
\texttt{svnversion}, which allows the compile-time SVN version number to
be included in the executable (and hence the output of the program). This
is useful to remember which version you were using when looking at
results at a later date. If
\texttt{svnversion} is not available (and it
should be if you have downloaded the code via SVN), you may get an
error message, but the code should still compile.

\subsubsection{Serial}

First, compile the MPI stub library in the \texttt{mpi\_s}
directory. Do this by editing the Makefile, and checking the compiler
is appropriate. You should be able to build the library and run the
tests using, e.g.,:

\begin{verbatim}
$ make libc
gcc -Wall -I.  -c mpi_serial.c
ar -cru libmpi.a mpi_serial.o
$ make testc
gcc -Wall   mpi_tests.c -L. -lmpi
./a.out
Running mpi_s tests...
Finished mpi_s tests ok.
\end{verbatim}

Now compile the main code in the \texttt{src} directory. Again
edit the Makefile to check the compiler. At this stage, you also
need to choose the LB model using exactly one of the preprocessor
options for D2Q9 (fluid only problems), D3Q15, or D3Q19. Now type,
e.g., using D3Q19:

\begin{verbatim}
$ make serial
gcc  -D SVN_REVISION='"'`svnversion`'"' -c svn.c
gcc  -D_D3Q19_ -O3 -Wall -I. -I../mpi_s -c d2q9.c
gcc  -D_D3Q19_ -O3 -Wall -I. -I../mpi_s -c d3q15.c
gcc  -D_D3Q19_ -O3 -Wall -I. -I../mpi_s -c d3q19.c
gcc  -D_D3Q19_ -O3 -Wall -I. -I../mpi_s -c model.c
...
\end{verbatim}

This should provide an executable \texttt{Ludwig.exe} which is linked
against the MPI stub library.

\subsubsection{Parallel}

Here, you do not need to compile the stub library. Simply compile
the main code with, e.g.,:
\begin{verbatim}
$ make mpi
mpicc -D_D3Q19_ -O3 -Wall -I. -c d2q9.c
mpicc -D_D3Q19_ -O3 -Wall -I. -c d3q15.c
mpicc -D_D3Q19_ -O3 -Wall -I. -c d3q19.c
mpicc -D_D3Q19_ -O3 -Wall -I. -c model.c
...
\end{verbatim}

Invoke the executable with the MPI launcher in the usual way for your
system, e.g., \texttt{mpirun -np 8 ./Ludwig.exe} for 8 processors,
and so on.

\subsubsection{ANSI C}

The code is ANSI C (1989), with the single exception of calls to the
library function \texttt{erfc()} in the Ewald sum code. This
can sometimes cause a problem, which can usually be solved with
a compiler-specific work-around.

\subsubsection{C assertions}

The code makes quite a lot of use of standard C assertions, which
are useful to prevent errors. They do result in a considerably
slower execution in some instances, so production runs should
switch off the assertions with the standard \texttt{NDEBUG}
preprocessor flag.

\section{User Input}

The executable will look for an input file at run time.
By default, this file is named \texttt{input} and should be in the
current working directory. The alternative is to specify the name
of the file explicitly on the command line:
\begin{verbatim}
$ ./Ludwig.exe input_file
\end{verbatim}
A reference input file \texttt{input.ref} is provided as a template.

@@

\subsection{Symmetric binary fluid}

\inputkey{free\_energy symmetric}

The following applies for the binary fluid problem with
compositional order parameter $\phi$ and free energy
(excluding the term in the density $\rho$):
\begin{equation}
 F[\phi] = 
\int dr \left(
{\textstyle \frac{1}{2}}A\phi^2
+ {\textstyle \frac{1}{4}}B\phi^4
+ {\textstyle \frac{1}{2}}\kappa (\mathbf{\nabla}\phi)^2 \right).
\end{equation}

This is described in some detail
by Kendon et al \cite{viv}. The first two terms represent the bulk
contribution, whereas the term in $\kappa$ penalises curvature in
the interface.

\inputkey{A} The parameter $A$. Note $A < 0$.

\inputkey{B} The parameter $B$. Note $B = -A$ for common usage,
although this is not enforced.

\inputkey{K} The parameter $\kappa$, which is positive.

The order parameter evolution is determined by a Cahn-Hilliard equation
with mobility set by

\inputkey{mobility} Sets mobility $M$ (uniform in space).

The following parameters control the initialisation of the order
parameter.

\inputkey{phi\_initialisation}

Determines how the compositional order parameter is initialised
at the start of the run. If set to \texttt{spinodal} the value
is set to $\phi_0$ as set above plus or minus a random noise, the
magnitude of which is set by the value of the \texttt{noise} key.
If set to \texttt{block} a one-dimensional profile is set up in
the $z$-direction representing two blocks of fluid with
$\phi = \pm 1$. The two interfaces are set at $z = L_z/4$ and
$z = 3L_z/4$ with the equilibrium $\tanh(z/\xi_0)$ profile having 
appropriate width. The $\phi = -1$ section is in the middle.

\inputkey{phi0}

The mean compositional order parameter roughly $-0.5 < \phi_0 < 0.5$.
The default value is zero, i.e., a symmetric 50:50 mixture by volume.

\inputkey{noise}

The magnitude of the initial fluctuations in $\phi$ used to
initiate spinodal decomposition.

\subsubsection{Binary fluid using two distributions}

\inputkey{symmetric\_lb}

This is the special case where the composition is represented
by a second LB distribution, and an appropriate lattice kinetic
equation approximating the Cahn-Hilliard equation is solved.
In this case the above parameters have the same meaning.

Note that the relaxation time for the second distribution is
related to the mobility by $tau_\phi = M\rho_0/\Delta t + 1/2$.

\subsection{Brazovskii}

\inputkey{free\_energy brazovskii}

This is similar to the symmetric free energy, but with one extra term
in a higher derivative of $\phi$.
\begin{equation}
 F[\phi] = 
\int dr \left(
{\textstyle \frac{1}{2}}A\phi^2
+ {\textstyle \frac{1}{4}}B\phi^4
+ {\textstyle \frac{1}{2}}\kappa (\mathbf{\nabla}\phi)^2
+ {\textstyle \frac{1}{2}} C (\nabla^2 \phi)^2 \right).
\end{equation}

The parameters now include $C$. For $A<0$, phase separation occurs
with a result depending on $\kappa$: ones get two symmetric phases
for $\kappa >0$ (cf. symmetric) or a lamellar phase for
$\kappa < 0$.

\inputkey{A} Bulk parameter $A < 0$.

\inputkey{B} Bulk parameter $B = -A$.

\inputkey{K} Negative for lamellar phase.

\inputkey{C} Positive.

Other parameters, including the mobility, are set as for the
symmetric free energy (see above).

\subsection{Surfactant in binary fluid}

\inputkey{free\_energy surfactant}

Currently under reconstruction.

This is for use with a two order parameter model the first of
which is the composition, as for the symmetric free energy,
while the second $\psi$ represents surfactant concentration.
The free energy density is made up of a number of terms:

\begin{equation}
{\textstyle \frac{1}{2}}A\phi^2
+ {\textstyle \frac{1}{4}}B\phi^4
+ {\textstyle \frac{1}{2}}\kappa (\mathbf{\nabla}\phi)^2
\end{equation}
is the standard symmetric term related to the composition.
These parameters are represented in the input as

\inputkey{surf\_A}
\inputkey{surf\_B}
\inputkey{surf\_kappa}

\begin{equation}
D \left(\psi \ln\psi + (1 - \psi) \ln(1-\psi)\right)
\end{equation}
represents the energy of surfactant in the bulk phase with surfactant
concentration $0 < \psi < 1$ with a single parameter $D$;
\begin{equation}
-{\textstyle \frac{1}{2}} \epsilon \psi (\mathbf{\nabla} \phi)^2
-{\textstyle \frac{1}{2}} \beta \psi^2  (\mathbf{\nabla} \phi)^2
\end{equation}
where the term in $\epsilon$ represents the energy reduction by
adsorbing surfactant at the interface and the term in $\beta$
provides an additional favourable term modelling the fact that
the molecules like to line up; finally, there is an extra term
\begin{equation}
+{\textstyle \frac{1}{2}} W \psi \phi^2
\end{equation}
which is included to stabilise the interface \cite{theissengompper}.

The corresponding keys for the input file are:

\inputkey{D} is the bulk surfactant contribution parameter

\inputkey{epsilon} is the parameter $\epsilon$

\inputkey{W} is the parameter $W$

\inputkey{beta} is the value of the parameter $\beta$.

\inputkey{phi\_b} the initial, uniform, background surfactant
concentration $\psi_b$.

\inputkey{mobility\_psi} Sets the (uniform) mobility for the surfactant
as appropriate for the Cahn-Hilliard equation.

\subsection{Polar Active Gel}

\inputkey{free\_energy polar\_active}

This models a polar active gel with vector order parameter $P_\alpha$.
The free energy density is:

The corresponding input parameters are:

\inputkey{polar\_active\_a}

\inputkey{polar\_active\_b}

\inputkey{polar\_active\_k}

\inputkey{polar\_active\_klc}

\inputkey{polar\_active\_zeta}

\inputkey{polar\_active\_lambda}

\inputkey{leslie\_ericksen\_gamma}

\inputkey{leslie\_ericksen\_swim}

\subsection{Liquid Crystal}

\inputkey{free\_energy lc\_blue\_phase}

Here, we have a tensor order parameter $Q_{\alpha\beta}$.
The free energy density is
\begin{eqnarray}
f = {\textstyle\frac{1}{2}}A_0(1 - \gamma/3)Q^2_{\alpha\beta}
  - {\textstyle\frac{1}{3}}A_0 \gamma
Q_{\alpha\beta}Q_{\beta\delta}Q_{\delta\alpha}
 + {\textstyle\frac{1}{4}}A_0 \gamma (Q^2_{\alpha\beta})^2
\nonumber
\\
+ {\textstyle\frac{1}{2}} \Big(
\kappa_0 (\epsilon_{\alpha\delta\sigma} \partial_\delta Q_{\sigma\beta} +
2q_0 Q_{\alpha\beta})^2 + \kappa_1(\partial_\alpha Q_{\alpha\beta})^2 \Big)
\end{eqnarray}

The corresponding input parameters are:

\inputkey{lc\_a0} The bulk free energy parameter $A_0$

\inputkey{lc\_gamma} The bulk free energy parameter $\gamma$

\inputkey{lc\_q0} The pitch wavenumber $q_0 = 2\pi / p$, where p
is the pitch.

\inputkey{lc\_kappa0} Elastic constant $\kappa_0$ in distortion free energy

\inputkey{lc\_kappa1} Elastic constant $\kappa_1$ in distortion free energy

Note that the code currently enforces the `one elastic constant'
approximation ($\kappa_0 = \kappa_1$), so both these values must
be equal in the input. This constraint may be relaxed in the future.

\inputkey{lc\_Gamma} The rotational diffusion constant appearing in
the Beris Edwards equation (note \texttt{lc\_gamma} and \texttt{lc\_Gamma}
are different).

\inputkey{lc\_xi} Aspect ratio for rod lie molecules appearing in the
stress tensor.

\inputkey{lc\_active\_zeta} Apolar liquid crystal activity constant.

\subsubsection{Initial LC order parameter $Q_{\alpha\beta}$}

\inputkey{lc\_q\_initialisation}

There are a number of useful choices here. The key value
\texttt{twist} initialises a simple cholesteric with the
helical axis in the $z-$direction, whereas the values 
\texttt{cholesteric\_x\_y\_z} provide similar initialisations 
with twist along the other axes.
The values \texttt{o8m} and \texttt{o2} give equilibrim BPI and BPII.
Another, cubic body-centered BP is obtained by the value \texttt{o5}.
Hexagonal BPs are initialised with \texttt{h2d, h3da} and \texttt{h3db}.\\
BPIII emerges from a start configuration of randomly positioned 
and oriented DTCs embedded into an isotropic or cholesteric environment.
This is initialised with the key value \texttt{bp3}, whereas the number
$N$ and radius $R$ of the DTCs and the type of the environment 
$ENV=\{0,1\}$, (0 = isotropic, 1 = cholesteric) is specified 
with the key value \texttt{lc\_init\_bp3} $N\_R\_ENV$. 
Note that calculations can become surprisingly unstable if the 
start configuration consits of too many and too large DTC-regions 
with respect to system size and decomposition.\\
The appropriate choices for the other parameters must be made correspondingly.

An additional \texttt{lc\_q\_init\_amplitude} value sets the
scalar order parameter  `amplitude' in each case. Typical
values are given in the input file. Values which are too large can
equally lead to instability.

\subsubsection{The redshift}

\inputkey{lc\_init\_redshift}

Sets the initial value of the redshift parameter. For example,
for the \texttt{o8m} initialisation, the redshift can be set to 0.83,
and for the \texttt{o2} initialisation, the redshift can be set to 0.91.
The default redshift is unity.

\inputkey{lc\_redshift\_update [0|1]}

Switches on (default is off) the dynamic computation of the redshift
from the order parameter gradient terms in the free energy. The
caluclation is performed at every time step, and override any
initial value specified in the above. It is also robust to restarts.

\subsection{Colloidal particles}

The are a number of important options required for colloids. If
none of these keys are present, no colloids will be used.

\inputkey{colloid\_init}

This determines how the code initialises particles (or not). As stated, the
default is to have no particles (value \texttt{no\_colloids}). There
are two other options at the moment.

There are two options:

\inputkey{colloid\_init    from\_file}

requires a preprepared file of colloid information. To understand
how to create such a file in the correct format,
see the example program \texttt{colloid\_file.c} in the util
directory.

\inputkey{colloid\_init   random}

This may be useful to initialise a limited number of colloids at
low volume fraction. Note that there is no guarantee that the
particles do not overlap, in which case the initialisation will
terminate. The number of particles and their properties
are determined by the value of the keys described below.

\inputkey{colloid\_type}

This controls the the type of particle. Appropriate values are
\texttt{inactive}, giving a standard fully resolved LB colloid;
\texttt{active} switches on the correction to BBL appropriate
for active particles (expecting parameters $b_1$ and $b_2$ to be
set); \texttt{subgrid} gives unresolved particles (radius $< 1$
lattice unit) and no BBL.

If more than one particle is used, all positions are set at random.

\inputkey{colloid\_gravity  0.0\_0.0\_-0.0001}

Sets a body force on each particle. Useful, for example, for
sedimentation. For example, the above gives a constant force in
the negative $z$-direction on each particle.
The code automatically computes the compensating body force on fluid
nodes required to give no net change in the total momentum of the
system at each time step.

\subsubsection{Interactions and the cell list}

In each local domain, colloidal particles are stored in a cell list.
This is a common structure in molecular dynamics-like problems. Here,
it also serves as the basis for parallel communication of colloid
information, so there are a number of constraints which it is important
to understand. In particular, parallel communication imposes the
constraint that there be at least 2 cells in the local domain in
each coordinate direction.

The size of the cells is computed automatically by the code based on
the local domain size, particle size, and the cut-off distance of any
pairwise interactions that are relevant. This will usually mean trying
to maximise the number of cells (to reduce pairwise interaction
calculation). The user must set the minimum allowable cell width.

\inputkey{colloid\_cell\_min}

This sets the minimum cell list width. This key must be set and there
must be at least two cells per processor domain. If the minimum does
not capture the specified interactions, a fatal error will result.
For spherical particles, the minimum width will typically be
$2a_h + h_c$ where $h_c$ is an interaction cut-off distance.

In the case where very large particles are required, it can be useful
to switch of the cell list. This is done via

\inputkey{colloid\_cell\_list\_interactions no}

The constraint in this case is that $2a_h + h_c < L_{local}$, ie.,
there is effectively one cell in each local domain. (In practice,
the constraint is slightly tighter than this if larger halo regions
are in effect.) This option
should not be required in normal circumstances.

\subsubsection{Initialisation from file}

A file containing initial state properties for one or more colloids
can be read at run file. This file must be of the correct from, but
can be ASCII or binary. To help to create such a file, an example
is given in \texttt{./util/colloid\_file.c}. This file will be
read correctly in both serial and in parallel. Colloid positions
should always be in terms of the global coordinates. By default,
the input expected is \texttt{config.cds.init.001-001}.

All colloid output is in serial (ie., a single file is produced)
at the moment. Again, it may be ASCII or binary.

\subsubsection{The colloid state}

The full data structure for the colloid state is defined in
\texttt{src/colloid.h} and the corresponding routines which read
and write the values are in \texttt{src/colloid.c}
(note colloid singular!). Most of the state corresponds clearly
with physical properties, although there are a number of 'structural'
elements which have no physical meaning. These include the
\texttt{rebuild} flag, which instructs the code to reconstruct the
boundary links if necessary, and \texttt{deltaphi} which is involved
in accounting for conserved order parameter in the \texttt{symmetric\_lb}
free energy. Further, not all the elements are relevant is all
circumstances: e.g., the magnetic dipole is only relevant is magnetic
interactions are required, and squirmer parameters are only relevant
to active particles.

Note that it is possible in principle to have magnetic active particles,
in which case the dipole direction (\texttt{s}) and the direction of
motion vector (\texttt{m}) are allowed to be distinct.

\subsubsection{Initialisation at random}

\inputkey{colloid\_random\_no} Sets the total number of particles

\inputkey{colloid\_random\_a0}

\inputkey{colloid\_random\_ah}

\inputkey{colloid\_random\_dh}

The parameter $a_0$ the nominal radius of the particle on the lattice.
This is used to construct the links for BBL. The smallest acceptable LB
particle is $a_0 = 1.25$ (approximately). There are 'magic' values
including 1.25, 2.3, 3.7, 4.77 which minimise discretisation effects.
The hydrodynamic radius of the particles is $a_h$. For all
reasonable applications choose $a_h = a_0$. This is the radius for
all physical purposes. The \texttt{colloid\_random\_dh} parameter
specifies the smallest allowed surface-surface separation if two or
more particles (or walls) are required. This is useful to prevent
very close particles experiencing large and destabilising interactions
at start time.

The other state for the initial colloids can be set uniformly by
means of the keys:

\inputkey{colloid\_random\_v0} initial velocity vector

\inputkey{colloid\_random\_w0} initial angular velocity vector

\inputkey{colloid\_random\_s0} initial spin vector (only relevant in magnetic
field)

The

\inputkey{colloid\_random\_m0} initial direction of motion vector for active
particles

\inputkey{colloid\_random\_b1} active parameter $b_1$

\inputkey{colloid\_random\_b2} active parameter $b_2$ (should be combined
with the \texttt{active} particle type key as discussed above).

The squirmer parameters specify the surface boundary conditions in
an approach originating with Lighthill \cite{lighthill} and Blake
\cite{blake}. Briefly, $b_1$ sets the propulsion speed
($U = {\frac{2}{3}} b_1$), while $b_2$ sets the
particle stresslet. The ratio $\beta = b_2/b_1$ determines the
mode of the squirmer motion; see \cite{isaac} for further details.

There is one special case. If you want exactly one particle, you may
set its initial position with

\inputkey{colloid\_random\_r0} the initial position vector.

This position must be within the current system, or no particle will
be created.

\subsubsection{Restarting at random!}

Be careful if you are restarting a simulation that used the random
initialisation at $t=0$. You must change to

\texttt{colloid\_init  from\_file}

to avoid generating a completely new set of random positions
(which will not be consistent with the density and order parameter
fields at the restart time). This is almost certainly not what you
intended!

\subsubsection{Hydrodynamic radius}

There is an important issue to understand about the (nominally)
spherical particles in LB. The input radius $a_0$ is used to
construct the link boundary conditions. However, discretisation
errors in the boundary conditions means that the `real' particle
size may be different. This real radius is the hydrodynamic radius $a_h$.
As a further complication, the hydrodynamic radius can also
be a function of viscosity for a given input radius. Some values
are given in Table~X. This values are computed using a calibration
procedure described by Nguyen and Ladd \cite{nguyen-ladd2002}.

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
$\eta$ & \multicolumn{3}{c|}{$a_0$}\\ \cline{2-4} 
       & 1.25 & 2.30 & 4.77 \\
\hline
1/6  & 1.09 (1.05) & 2.23 (2.20) & 4.76 \\
1/100  & 1.40 (1.34) & 2.50 (2.46) & 5.01 \\
1/1000  & 1.63 & 2.71 & 5.23 \\
\hline
\end{tabular}
\end{center}
\caption{A table of calibrated hydrodynamic radii as a function of input
radius and fluid viscosity $\eta$. These figures are for D3Q19 (and D3Q15
in brackets).}
\end{table}

If a calibration is required for a given radius and viscosity,
use the \texttt{calibration on} key pair in the input file. Some
examples are given in the \texttt{tests/calibration} directory.
An apppropriate
number of time steps must be used to allow the system to get over
the initial transient (we use the momentum diffusion time for the
system $L^2/\eta$) and to allow at least one
particle Stokes time ($a/U$). The input radius and hydrodynamic
radius should be set the same in the input file.

% PENDING Ginzburg d'Humieres correct to ghost mode relaxation times

@@

\subsubsection{Flat wall lubrication correction}

It is possible to prevent colloids colliding with the flat boundary walls
by adding the correction to the normal component of the lubrication
force. The general form of this correction is
\begin{equation}
\mathbf{F}_{\mathrm{lub}} = -6\pi \eta a_h^2
%({\textstyle \frac{1}{h} - \frac{1}{h_c}})
(1/h - 1/h_c)
\mathbf{u} . \mathbf{r}.
\end{equation}
Here, $h$ is the surface to surface separation, and $h_c$ is the cutoff
distance beyond which the correction is not applied. The relative
velocity (assuming the wall is not moving) and normal separation are
$\mathbf{u}$ and $\mathbf{r}$ respectively.

The cutoff distance can be set from the input via

\inputkey{boundary\_lubrication\_rcnormal 0.1}

where the value is (strictly) set via calibration, cf. the hydrodynamic
radius. In general, the cutoff is between zero and 0.5 lattice spacing,
and can be smaller for larger particles. Because the wall velocity is
fixed, this force correction should cause no stability issues in the
colloid velocity update (provided a colloid's initial position is not
very close to the wall). By default the cutoff $h_c = 0$.

\subsection{Lees-Edwards planes}

@@

\section{Parallel Performance}

\subsection{General Comments}

\subsection{Things to Remember and Things to Avoid}
\label{section-advice}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  user.tex
%
%  The 'user' section which holds an overview, and discusses
%  compilation and running.
%
%  $Id: user.tex 1694 2012-06-28 09:44:12Z stratford $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2010 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Basic User Input}

\subsection{Parallel Performance}

\subsubsection{General Comments}

\subsubsection{Things to Remember and Things to Avoid}
\label{section-advice}

The executable will look for an input file at run time.
By default, this file is named \texttt{input} and should be in the
current working directory. The alternative is to specify the name
of the file explicitly on the command line:
\begin{verbatim}
$ ./Ludwig.exe input_file
\end{verbatim}

A reference input file \texttt{input.ref} is provided as a template.

@@

@@

\subsubsection{Lees-Edwards planes}

@@
